Introducing Distributed Dynamic Data-intensive (D3) Science: Understanding Applications and Infrastructure

### 2015-09-13 3dpas_intro.tex
checkpoint

The landscape of scientific and enterprise computing is being fundamentally
altered by the prodigious volumes of data.  Not only are the volumes of data
produced by scientific applications increasing rapidly, there is also a
corresponding increase in the amount of data that needs to be processed and
analyzed.  With the increase in data volumes, types, and sources of data, an
important concomitant development has been an increase in the requirement for
and complexity of the infrastructure needed to support these requirements.
Furthermore, data are often naturally distributed and have to be processed in
situ; occasionally data that are localized have to be distributed in order to be
processed, either for reasons of performance or for collaborative analytics.
The scale and significance of varying data source/destination and
transfer/production rates makes temporal variations important, which in turn
eventually impact the design and development of infrastructure to support them:
resource scheduling, data placement, and transfer decisions that were statically
determinable at small scales, emerge as dynamic and important considerations at
large scales of data and distribution.

@@

The challenges of distributed data-intensive applications span beyond the
management and curation of large volumes of data. A critical requirement is to
make sense of this data, i.e., transform the data into information en route to
assembling knowledge. Among other things, the transformation from data to
information requires extensive amounts of computational processing of the data;
thus the data-intensive nature of the data-intensive science problem is strongly
coupled with compute-intensive requirements.  As the data are often distributed,
a consequence is that many attributes of distributed systems permeate to data.

>>>>

The landscape of scientific and enterprise computing is being fundamentally
altered by the prodigious volumes of data.  % Not only are the volumes of data
% produced by scientific applications increasing rapidly, there is also a
% corresponding increase in the amount of data that needs to be processed and
% analyzed.
With the increase in data volumes, types, and sources of data, an
important concomitant development has been an increase in the requirement for
and complexity of the infrastructure needed to support these requirements.
Furthermore, data are often naturally distributed and have to be processed in
situ; occasionally data that are localized have to be distributed in order to be
processed, either for reasons of performance or for collaborative analytics.
The scale and significance of varying data source/destination and
transfer/production rates makes temporal variations important, which in turn
eventually impact the design and development of infrastructure to support them:
resource scheduling, data placement, and transfer decisions that were statically
determinable at small scales, emerge as dynamic and important considerations at
large scales of data and distribution.

@@

The challenges of distributed data-intensive applications span beyond the
management and curation of large volumes of data. A critical requirement is to
make sense of this data, i.e., transform the data into information en route to
assembling knowledge. Among other things, the transformation from data to
information requires extensive amounts of computational processing of the data;
thus the data-intensive nature of the data-intensive science problem is strongly
coupled with compute-intensive requirements.

% As the data are often distributed, a consequence is that many attributes of
% distributed systems permeate to data.
